Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-12-11 paper/aldebaran.tex
bedding
new address

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Sydney Institute for Astronomy, School of Physics, University of Sydney, Sydney NSW 2006, Australia} 
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}

@@

We would like to thank David Hogg and Dan Foreman-Mackey for their helpful discussions.

>>>>

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Sydney Institute for Astronomy, School of Physics, University of Sydney, Sydney NSW 2006, Australia} 
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}

@@

We would like to thank Tim Bedding, David Hogg and Dan Foreman-Mackey for their helpful discussions.
